---
title: "Maternal Health Risk Predictor"
bibliography: refs.bib
output: 
  github_document:
    toc: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
library(kableExtra)
```

## Authors

- Lennon Au-Yeung
- Chenyang Wang
- Shirley Zhang

(Team 14) 

# Summary

This data analysis project was created in fulfillment of the team project requirements for DSCI 522 (Data Science Workflows), a course in the Master of Data Science program at the University of British Columbia.

# Introduction

Maternal mortality is a large risk in lower and lower middle-income countries, with about 810 women dying from preventable pregnancy-related causes each day (WHO, 2019). Often, there is a lack of information about the woman's health during pregnancy, making it difficult to monitor their status and determine whether they may be at risk of complications (Ahmed and Kashem, 2020). A potential solution to this issue is through using the 'Internet of Things (IoT)', or physical sensors which can monitor and report different health metrics of a patient to their health care provider. Medical professionals can then analyze this information to determine whether a patient may be at risk. 

For this project, we aim to answer the question: 

> **"Can we use data analysis methods to predict the risk level of a patient during pregnancy (low, mid, or high) given a number of metrics describing their health profile?"** 

This is an important question to explore given that human resources are low in lower income countries, and non-human dependent classification methods can help provide this information to more individuals. Furthermore, classifying a patient's risk level through data-driven methods may be advantageous over traditional methods which may involve levels of subjectivity. 

IoT sensors can collect a diverse range of health metrics, however not all of them may be useful in predicting whether a patient is at risk of adverse health outcomes. Thus, we also hope to use data analysis methods to infer (sub-question) whether some metrics may be more important in determining maternal health risk levels than others. 

# Methods 

## Data 


## Planned Analysis


# Results

## Exploratory Data Analysis 
- first image shows the distribtion across target classes, as we can see from the bar chart below, there is not a  drastic class imbalanace in the training data, however, we will still explore whether a balanced class weight will improve our model performance.

- The second image is the density distribution across all features, which could provideus with insights on whether the distribution of some features are different for different target classes. 

## Model Building
- try models 1. dummy classfier 2. decision tree 3. SVM 4. logistic regression 5. KNN
For all the model, use default parameter, did not inclue hyperpamater optimization.(include table of model compare) table 1.Choose decision because it has highest crossvalidation score.
```{r load data}
model_comparison <- read.csv("../src/maternal_risk_model_figures/model_comparison_table.csv", row.names=1, heade=TRUE)
kable(model_comparison)
```

- hyperpamater optimization
use random search, try different max depth 1 and 50, best is 29, include plot_3 hyperpar_plot,

- score at the test data, the score is 0.823

- confusion matrix, incluse table_2(test_data_confusion_matrix),

# Assumptions and Limitations

# Future Directions


# References